### 2015-07-09 2015-compmorphon-morphver/poster.tex
some minor changes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61229 72bbbca6-d526-0410-a7d9-f06f51895060

		\htwo{Reasons for being \hilitetwo{incomplete}}
		\begin{itemize}
			\item restrictions of the medium (e.g., number of pages)
			\item limitations of introspection, working with native speakers
			\item \textbf{lack of automatic testing}
		\end{itemize}
	}

@@

		\htwo{Framework:\ HFST}
		\begin{itemize}
			\item Reimplements Xerox FST formalisms ({\tt lexc} \& {\tt twol})
			\item Also provides a wrapper around popular free/open-source FST toolkits: SFST, OpenFST, and Foma
		\end{itemize}
		\htwo{Approach}
		\begin{itemize}
			\item two-level method \parencite{koskenniemi83}
			\item morphotactics implemented in \texttt{lexc}
			\item morphophonology implemented in \texttt{twol} (SPE-style rules)
			\item compiled separately; compose-intersected to single transducer\vspace{-0.1ex}\\
			алдым\hfill{}\hilitetwo{↔}\hfill{}\texttt{ал\hilitegrey{>}\archiphon{D}\archiphon{I}\hilitegrey{>}м}\hfill{}\hilitetwo{↔}\hfill{}\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}}\vspace{-0.1ex}\\
			алдым\hfill{}\hilitetwo{↔}\hfill{}\texttt{алд\hilitegrey{>}\archiphon{I}м}\hfill{}\hilitetwo{↔}\hfill{}\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}
		\end{itemize}

@@

					\begin{itemize}
						\item \textcite[22-23]{andersonharrison99} %Anderson and Harrison (1999, pp.\ 9, 22-23)
					\end{itemize}
					\includegraphics[width=0.49\textwidth]{img/andersonharrison9}\\
					\includegraphics[width=0.49\textwidth]{img/andersonharrison22-23}
					\begin{itemize}
						\item \textcite[117-118]{isxakovpalmbax61} %Исхаков, Ф.Г.; Пальмбах (1961, pp.\ 117-118)
					\end{itemize}
					\includegraphics[width=0.49\textwidth]{img/isxakovpalmbax117}

				\htwo{More complete characterisation}
				\begin{itemize}
					\item /k/ ‹к› elides at the end of >1-σ stems intervocalically\\
						инэк+I → инээ, өк+I → өгү
					\item /g/ ‹г› elides at the end of any stem intervocalically\\
						өг+I → өө 
					\item /ŋ/ ‹ң› elides at the end of \textbf{some} stems intervocalically.\\
						\textbf{соң+I → соо}, чаң+I → чаңы, түң+I → түңү
				\end{itemize}

@@

				But not part of the morphophonological description.\\
				(A. \& H., p.\ 35)\hfill{}\includegraphics[width=0.2\textwidth]{img/andersonharrison35}\\
				(И.\ \& П., p.\ 447)\hfill{}\includegraphics[width=0.35\textwidth]{img/isxakovpalmbax447}

@@

		\headerbox{Example: Tuvan vowel harmony}{name=tuvanvowelharmony,column=3}{ %{name=otherexamples,column=1,span=2,below=tuvanvelars}{ % after consonant clusters in loanwords
			%\begin{multicols}{2}
				\htwo{Tuvan vowel harmony}
					\begin{itemize}
						\item High and low vowels harmonise in backness\\
						киж\hiliteone{и}\tag{n}\tag{pl}\tag{acc}: киж\hiliteone{и}л\hiliteone{е}рн\hiliteone{и}, н\hilitetwo{о}м\tag{n}\tag{pl}\tag{acc}: н\hilitetwo{о}мн\hilitetwo{а}рн\hilitetwo{ы}
						\item High vowels also harmonise in roundness\\
						round: \hiliteone{ө}г\tag{n}\tag{acc}:\ \hiliteone{ө}гн\hiliteone{ү}, \hilitetwo{о}й\tag{n}\tag{acc}:\ \hilitetwo{о}йн\hilitetwo{у}\\
						unround: ү\hiliteone{е}\tag{n}\tag{acc}:\ ү\hiliteone{е}н\hiliteone{и}, \hilitetwo{а}й\tag{n}\tag{acc}:\ \hilitetwo{а}йн\hilitetwo{ы}
					\end{itemize}
				\htwo{Initial implementation (high-vowels)}

@@

		\htwo{Attested system}
			\begin{itemize}
				\item Some adjectives may not be substantivised
				\item Some adjectives may not be used adverbially
				\item Some adjectives do not have comparative forms
				\item …a range of “adjective classes” in most Turkic languages
			\end{itemize}
		\htwo{Implementation:\ proper categorisation}
			\begin{itemize}
				\item only correct forms are analysed and generated
			\end{itemize}

>>>>

		\htwo{Reasons for being \hilitetwo{incomplete}}
		\begin{itemize}
			\item restrictions of the medium (e.g., number of pages)
			\item limitations of introspection and working with native speakers
			\item \textbf{lack of automatic testing}
		\end{itemize}
	}

@@

		\htwo{Framework:\ HFST}
		\begin{itemize}
			\item Reimplements Xerox FST formalisms ({\tt lexc} \& {\tt twol})
			\item Also provides a wrapper around popular free/open-source FST toolkits: SFST, OpenFST, and Foma
		\end{itemize}
		\htwo{Approach}
		\begin{itemize}
			\item two-level method \parencite{koskenniemi83}
			\item \textbf{morphotactics} implemented in \texttt{lexc}
			\item \textbf{morphophonology} implemented in \texttt{twol} (SPE-style rules)
			\item compiled separately; compose-intersected to single transducer\vspace{-0.1ex}\\
			алдым\hfill{}\hilitetwo{↔}\hfill{}\texttt{ал\hilitegrey{>}\archiphon{D}\archiphon{I}\hilitegrey{>}м}\hfill{}\hilitetwo{↔}\hfill{}\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}}\vspace{-0.1ex}\\
			алдым\hfill{}\hilitetwo{↔}\hfill{}\texttt{алд\hilitegrey{>}\archiphon{I}м}\hfill{}\hilitetwo{↔}\hfill{}\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}
		\end{itemize}

@@

					\begin{itemize}
						\item \textcite[9, 22-23]{andersonharrison99} %Anderson and Harrison (1999, pp.\ 9, 22-23)
					\end{itemize}
					\includegraphics[width=0.49\textwidth]{img/andersonharrison9}\\
					\includegraphics[width=0.49\textwidth]{img/andersonharrison22-23}
					\begin{itemize}
						\item \textcite[117-118]{isxakovpalmbax61} %Исхаков, Ф.Г.; Пальмбах (1961, pp.\ 117-118)
					\end{itemize}
					\includegraphics[width=0.49\textwidth]{img/isxakovpalmbax117}

				\htwo{More complete characterisation}
				\begin{itemize}
					\item /k/ ‹к› elides at the end of >1-σ stems intervocalically..\\
						инэк+I → инээ, өк+I → өгү
					\item /g/ ‹г› elides at the end of any stem intervocalically\\
						өг+I → өө 
					\item /ŋ/ ‹ң› elides at the end of \textbf{some} stems intervocalically\\
						\textbf{соң+I → соо}, чаң+I → чаңы, түң+I → түңү
				\end{itemize}

@@

				But not part of the morphophonological descriptions.\\
				(A. \& H., p.\ 35)\hfill{}\includegraphics[width=0.2\textwidth]{img/andersonharrison35}\\
				(И.\ \& П., p.\ 447)\hfill{}\includegraphics[width=0.35\textwidth]{img/isxakovpalmbax447}

@@

		\headerbox{Example: Tuvan vowel harmony}{name=tuvanvowelharmony,column=3}{ %{name=otherexamples,column=1,span=2,below=tuvanvelars}{ % after consonant clusters in loanwords
			%\begin{multicols}{2}
				\htwo{Tuvan vowel harmony}
					\begin{itemize}
						\item High and low vowels harmonise in \hilitetwo{back}ness\\
						киж\hiliteone{и}\tag{n}\tag{pl}\tag{acc}: киж\hiliteone{и}л\hiliteone{е}рн\hiliteone{и}, н\hilitetwo{о}м\tag{n}\tag{pl}\tag{acc}: н\hilitetwo{о}мн\hilitetwo{а}рн\hilitetwo{ы}
						\item High vowels also harmonise in roundness\\
						round: \hiliteone{ө}г\tag{n}\tag{acc}:\ \hiliteone{ө}гн\hiliteone{ү}, \hilitetwo{о}й\tag{n}\tag{acc}:\ \hilitetwo{о}йн\hilitetwo{у}\\
						unround: ү\hiliteone{е}\tag{n}\tag{acc}:\ ү\hiliteone{е}н\hiliteone{и}, \hilitetwo{а}й\tag{n}\tag{acc}:\ \hilitetwo{а}йн\hilitetwo{ы}
					\end{itemize}
				\htwo{Initial implementation (high-vowels)}

@@

		\htwo{Attested system}
			\begin{itemize}
				\item Some adjectives may not be substantivised
				\item Some adjectives may not be used adverbially
				\item Some adjectives do not have comparative forms
				\item …a range of “adjective classes” in most Turkic languages
			\end{itemize}
		\htwo{Implementation:\ proper categorisation}
			\begin{itemize}
				\item only correct forms are analysed and generated (Tatar exs.)
			\end{itemize}
